---
title: "RBI"
author: "Santhosh Kumar Krishnan"
date: "5/21/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---
1.READ DATA AND INSTALL LIBRARIES
```{r}
RBI <- read.csv("D:/Data Science/Dr Vinod online classes/Class 5-Cluster/RBI.csv")
head(RBI,3)
library(dplyr)
library(factoextra)
library(cluster)
```

2.REMOVE THE RESPONSE VARIABLE

```{r}
df <- RBI[,-1]
rownames(df) <- RBI[,1]
head(df,3)
```

3.CHECK NAs AND SCALE THE DATA

```{r}
summary(df)#no NAs
df <- scale(df)#scaled data
head(df)
```

4.FIND EUCLIDEAN DIST FOR SAMPLE DATA

```{r}
ind <- sample(1:nrow(df),15,replace = T)
df15 <- df[ind,]
df15_dist <- dist(df15)


```

5.CHECK FOR CLUSTER FORMATION

```{r}
fviz_dist(df15_dist)
```

6.NUMBER OF CLUSTER USING WSS

```{r}
fviz_nbclust(df,kmeans,method='wss')+geom_vline(xintercept = 5,linetype=7,col='green')
```

7.K MEANS

```{r}
df.km=kmeans(df,5,nstart=20)
df.km
df.km$cluster
```

8.ADD MEMBERSHIP TO THE DATA

```{r}
RBI_1 <- cbind(RBI,Clusters=df.km$cluster)
head(RBI_1,3)
```

9.HEIRARCHICAL CLUSTEING

```{r}
df.dist <- dist(df,method="euclidean")
df.hc <- hclust(df.dist,method='ward.D2')
```

10.VISUALIZE DENDOGRAM

```{r}
fviz_dend(df.hc)
```

11.CLUSTERING USING CUTREE

```{r}
grp <- cutree(df.hc,k=5)
```

12.ADD MEMBERSHIP TO THE DATA

```{r}
RBI_2 <- cbind(RBI,clusters=grp)
head(RBI_2,3)
```

13.COMPARISION OF KMEANS AND HCLUST

```{r}
table(df.km$cluster,grp)

```

14.K MEANS CLUSTERING

```{r}
fviz_cluster(list(cluster=grp, data = df), palette = "jco",ggtheme = theme_classic())
```

15.HIERARCHICAL CLUSTERING

```{r}
fviz_cluster(df.km, data = df, palette = "jco",ggtheme = theme_minimal())
```
16.PROFILING KMEANS AND HCLUST GROUPS OF ORIGINAL DATA

```{r}
aggregate(RBI[,-1],by=list(df.km$cluster),mean)
aggregate(RBI[,-1],by=list(grp),mean)

```


CONCLUSION
1.Kmeans Clustering has 5 clusters of sizes 10,13,6,2,5.

2.Heirarchical clustering 5 clusters of sizes 10,14,6,2,4.